Caring and Feeding the Wild Caught Data

### 2021-03-03 report_alt.Rmd
arxiv version

---
title: "Caring and Feeding the Wild Caught Data"
subtitle: "A Case of The NLSY79 Data"
author: "Dewi Amaliah, Dianne Cook, Emi Tanaka, Nicholas Tierney, Kate Hyde"
date: "24/02/2021"
output: 
  bookdown::pdf_document2:
    toc : false
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache = TRUE, 
                      cache.path = "cache/")
library(tidyverse)
library(brolgar)
library(patchwork)
library(kableExtra)
library(MASS)
library(janitor)
```

@@

```{r featureplot, echo = FALSE, fig.cap = "a) Pattern of Mean Hourly Wage of High School Cohort; b) The Three Features of the Cohort", fig.width=6, fig.height=4}

>>>>

---
title: "Caring and Feeding the Wild Caught Data"
subtitle: "A Case of The NLSY79 Data"
authors:
  - name: Dewi Amaliah
    thanks: ""
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: ""
  - name: Kate Hyde
    thanks: ""
    department: ""
    affiliation: ""
    location: ""
    email: ""
  - name: Emi Tanaka
    thanks: emitanaka.org
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: emi.tanaka@monash.edu
  - name: Nicholas Tierney
    thanks: ""
    department: ""
    affiliation: ""
    location: ""
    email: ""
  - name: Dianne Cook
    thanks: dicook.org
    department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    location: Clayton, VIC 3800
    email: dicook@monash.edu
bibliography: references.bib
biblio-style: unsrt
#preamble: >
output: 
  rticles::arxiv_article:
    keep_tex: false
date: "24/02/2021"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE,
                      cache = TRUE, 
                      cache.path = "cache/",
                      fig.path = "figures/")
library(tidyverse)
library(brolgar)
library(patchwork)
library(kableExtra)
library(MASS)
library(janitor)
```

@@

```{r featureplot, echo = FALSE, fig.cap = "a) Pattern of Mean Hourly Wage of High School Cohort; b) The Three Features of the Cohort", fig.width=6, fig.height=4, cache = FALSE}
